### 2011-06-09 thesis/macros.tex
Added coments on how does the sampling method to have a constant P(novel) looks like.
Added more discussion on how P(novel) is dependent on structure.

@@

\tikzset{latent/.style={circle,fill=white,draw=red,thick,inner sep=1pt, 
minimum size=20pt, font=\fontsize{10}{10}\selectfont},
obs/.style={latent,fill=gray!25},
const/.style={rectangle, inner sep=0pt},
factor/.style={rectangle, fill=red,minimum size=7pt, inner sep=0pt},
-/.style={color=red, thick},
>={triangle 45}}

>>>>

\newtheorem{algorithm}{Algorithm}

@@

\tikzset{latent/.style={circle,fill=white,draw=red,thick,inner sep=1pt, 
minimum size=20pt, font=\fontsize{10}{10}\selectfont},
obs/.style={latent,fill=gray!25},
const/.style={rectangle, inner sep=0pt},
factor/.style={rectangle, fill=red,minimum size=7pt, inner sep=0pt},
yellow/.style={latent,minimum size=15pt,fill=yellow!75},
blue/.style={latent,minimum size=15pt,fill=blue!75},
-/.style={color=red, thick},
>={triangle 45}}

### 2011-06-09 thesis/novelty.tex
Added more discussion on how P(novel) is dependent on structure.

\begin{figure}[h]
\caption{\label{fig:structure-influences-novelty}Example showing how
         structure can influence $P(novel)$}
\end{figure}

>>>>

\begin{figure}[h]

\centering

\subfloat[Training Data]{
\begin{tikzpicture}
  \node [matrix,matrix anchor=mid, column sep=15pt, row sep=10pt,ampersand replacement=\&] {
    \node (a) [blue] {}; \& \node (e) [yellow] {}; \\
    \node (b) [yellow] {}; \& \node (f) [blue] {}; \\
    \node (c) [blue] {}; \& \node (d) [yellow] {}; \\
  };
  \draw [-] (a) -- (e) -- (f) -- (d) -- (c) -- (b) -- (f);
\end{tikzpicture}
\quad
\begin{tikzpicture}
  \node [matrix,matrix anchor=mid, column sep=15pt, row sep=10pt,ampersand replacement=\&] {
    \node (a) [yellow] {}; \& \node (e) [blue] {}; \\
    \node (empty) [blue,fill=none,draw=none] {}; \& \\
    \node (c) [blue] {}; \& \node (d) [yellow] {}; \\
  };
  \draw [-] (c) -- (a) -- (d) -- (e);
\end{tikzpicture}
\begin{tikzpicture}
  \node [matrix,matrix anchor=mid, column sep=15pt, row sep=10pt,ampersand replacement=\&] {
    \node (a) [yellow] {}; \& \node (e) [blue] {}; \\
    \node (b) [blue] {}; \& \node (f) [yellow] {}; \\
    \node (c) [yellow] {}; \& \node (d) [blue] {}; \\
  };
  \draw [-] (a) -- (e) -- (f) -- (d) -- (c) -- (b) -- (a);
\end{tikzpicture}
\quad
\begin{tikzpicture}
  \node [matrix,matrix anchor=mid, column sep=15pt, row sep=10pt,ampersand replacement=\&] {
    \node (a) [blue] {}; \& \node (e) [yellow] {}; \\
    \node (b) [yellow] {}; \& \node (f) [blue] {}; \\
    \node (c) [blue] {}; \& \node (d) [blue] {}; \\
  };
  \draw [-] (c) -- (b) -- (a) -- (e) -- (f) -- (b);
  \draw [-] (b) -- (d);
\end{tikzpicture}
\quad
\begin{tikzpicture}
  \node [matrix,matrix anchor=mid, column sep=15pt, row sep=10pt,ampersand replacement=\&] {
    \node (a) [yellow] {}; \& \node (e) [blue] {}; \\
    \node (b) [blue] {}; \& \node (f) [yellow] {}; \\
    \node (c) [yellow] {}; \& \node (d) [blue] {}; \\
  };
  \draw [-] (e) -- (a) -- (b) -- (c) -- (d);
  \draw [-] (b) -- (f);
\end{tikzpicture}

}

\subfloat[Sample A\label{fig:sample-a}]{
\begin{tikzpicture}
  \node [matrix,matrix anchor=mid, column sep=15pt, row sep=10pt,ampersand replacement=\&] {
    \node (a) [latent] {$a$}; \& \node (b) [latent] {}; \\
    \node (c) [latent] {};    \& \node (d) [latent] {}; \\
  };
  \draw [-] (a) -- (b) -- (d) -- (c) -- (a);
\end{tikzpicture}
}
\qquad
\subfloat[Sample B\label{fig:sample-b}]{
\begin{tikzpicture}
  \node [matrix,matrix anchor=mid, column sep=15pt, row sep=10pt,ampersand replacement=\&] {
    \node (a) [latent] {$a$}; \& \node (b) [latent] {}; \\
    \node (c) [latent] {};    \& \\
  };
  \draw [-] (a) -- (b) -- (c) -- (a);
\end{tikzpicture}
}

\caption{\label{fig:structure-influences-novelty}Given that the only known
         classes are yellow and blue, and that two nodes of the same class
         were never found connected together, it is reasonable to assume
         that on sample B the probability of node $a$
         be a novel class is greater than on sample A.}
\end{figure}
